Modelling the Lymphatic Metastatic Progression Pathways of OPSCC \\ from Multi-Institutional Datasets

### 2024-02-20 src/tex/ms.tex
[showyourwork] overleaf sync

\usepackage{showyourwork}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{wasysym}
\usepackage{xcolor}
\usepackage{nicefrac}
\usepackage{multirow}
\usepackage[affil-it]{authblk}
\usepackage{graphicx}
\usepackage{biblatex}
\addbibresource{bib.bib}

@@

A patient's state of (hidden) lymphatic involvement at time $t$ is described as a collection of binary \glspl{rv}, one for each of the $V$ \glspl{lnl}:
%
\begin{equation}
    \mathbf{X}[t] = \left( X_v[t] \right) \qquad v \in \left\{ 1,2, \ldots, V \right\}
\end{equation}
%
Each of the \glspl{lnl} can be in the state $X_v=0$ (\texttt{FALSE}), meaning \gls{lnl} $v$ is healthy, or in the state $X_v=1$ (\texttt{TRUE}), indicating the \gls{lnl} harbors metastases. The involved state includes occult disease.

@@

The model evidences of all candidate graphs are reported in \cref{table:evidence}. A visual ranking is provided in \cref{fig:ranking}. Let us first consider the six models in which one of the candidate arcs is added to the base graph. Evidently, adding a connection from \gls{lnl} I to II is strongly supported given this dataset, and is slightly superior to the reverse connection from \gls{lnl} II to I. In addition, there is strong evidence for introducing an arc from \gls{lnl} IV to V. Furthermore, there is substantial evidence for an arc from \gls{lnl} III to V. All other investigated additions lead to improvements that are barely worth a mention or do not justify the additional complexity at all, indicated by a lower evidence.

@@

The patient data detailing lymphatic involvement is publicly available in the form of CSV tables in the GitHub repository \href{https://github.com/rmnldwg/lydata}{\texttt{rmnldwg/lydata}}. In another GitHub repository, \href{https://github.com/rmnldwg/lynference}{\texttt{rmnldwg/lynference}}, we define the experiments based on different graph structures. These experiments are reproducible via the tool \href{https://dvc.org}{DVC} and their locally computed results are uploaded to an Azure blob storage container. Lastly, the \LaTeX\ source code, all Python scripts to generate the figures and tables in this work, and the pipeline definition to build the document (using \showyourwork \cite{luger_mapping_2021}) are made public in the GitHub repository \href{https://github.com/rmnldwg/graph-extension-paper}{\texttt{rmnldwg/graph-extension-paper}}. To rebuild it, the \showyourwork tool first pulls the patient data from the \href{https://github.com/rmnldwg/lydata}{\texttt{rmnldwg/lydata}} repository and the trained models in the form of \gls{mcmc} samples from the Azure blob storage container, then runs the Python scripts, and finally compiles the \LaTeX\ article. Detailed instructions on how to reproduce the entire pipeline, including the individual experiments, may be found in the respective repository's \texttt{README.md} file. We also gladly provide support for any effort to repr

>>>>

\usepackage{showyourwork}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{wasysym}
\usepackage{xcolor}
\usepackage{nicefrac}
\usepackage{multirow}
\usepackage[affil-it]{authblk}
\usepackage{graphicx}
\usepackage[
    maxalphanames=6,
    style=nature,
    backend=biber
]{biblatex}
\addbibresource{bib.bib}

@@

A patient's state of (hidden) lymphatic involvement at time $t$ is described as a collection of binary \glspl{rv}, one for each of the $V$ \glspl{lnl}:

\begin{equation}
    \mathbf{X}[t] = \left( X_v[t] \right) \qquad v \in \left\{ 1,2, \ldots, V \right\}
\end{equation}
%
Each of the \glspl{lnl} can be in the state $X_v=0$ (\texttt{FALSE}), meaning \gls{lnl} $v$ is healthy, or in the state $X_v=1$ (\texttt{TRUE}), indicating the \gls{lnl} harbors metastases. The involved state includes occult disease.

@@

The model evidences of all candidate graphs are reported in \cref{table:evidence}. For the graph with the highest and lowest model evidence, the expected log-accuracy is plotted against the inverse temperature in \cref{fig:thermo_int}. A visual ranking is provided in \cref{fig:ranking}. Let us first consider the six models in which one of the candidate arcs is added to the base graph. Evidently, adding a connection from \gls{lnl} I to II is strongly supported given this dataset, and is slightly superior to the reverse connection from \gls{lnl} II to I. In addition, there is strong evidence for introducing an arc from \gls{lnl} IV to V. Furthermore, there is substantial evidence for an arc from \gls{lnl} III to V. All other investigated additions lead to improvements that are barely worth a mention or do not justify the additional complexity at all, indicated by a lower evidence.

@@

The patient data detailing lymphatic involvement is publicly available in the form of CSV tables in the GitHub repository \href{https://github.com/rmnldwg/lydata}{\texttt{rmnldwg/lydata}}. In another GitHub repository, \href{https://github.com/rmnldwg/lynference}{\texttt{rmnldwg/lynference}}, we define the experiments based on different graph structures. These experiments are reproducible via the tool \href{https://dvc.org}{DVC} and their locally computed results are uploaded to an Azure blob storage container. Lastly, the \LaTeX\ source code, all Python scripts to generate the figures and tables in this work, and the pipeline definition to build the document (using \showyourwork \cite{luger_mapping_2021}) are made public in the GitHub repository \href{https://github.com/rmnldwg/graph-extension-paper}{\texttt{rmnldwg/graph-extension-paper}}. To rebuild it, the \showyourwork tool first pulls the patient data from the \href{https://github.com/rmnldwg/lydata}{\texttt{rmnldwg/lydata}} repository and the trained models in the form of \gls{mcmc} samples from the Azure blob storage container, then runs the Python scripts, and finally compiles the \LaTeX\ article. Detailed instructions on how to reproduce the entire pipeline, including the individual experiments, may be found in the respective repository's \texttt{README.md} file. We also gladly provide support for any effort to reproduce our results.
